Comments on Latent Ranking

### 2020-08-31 output_scripts/aug_updates.Rmd
code to permute the cohorts and fit cmmhp and equivalent in rmd

<!-- # Shuffling the data -->

>>>>

# Shuffling the data

Another component of interest is ensuring that there is some 
structure in this model that would not be captured by 
random data. To see this, we can simply shuffle the nodes
involved in fights and look at the corresponding model fits,
which should not contain any information.

```{r shuffle cohort and stan fit, slow locally}
current_cohort <- 1

print(paste("Cohort",current_cohort))
###
stan_input_lst <- prepareData_permute_Stan(current_cohort)
### get the corresponding expert rank
permuted_data <- stan_input_lst$permuted_data

expert_rank_10_curr <- expertRankHierarchy(permuted_data)
stan_input_lst$alpha_id <- expert_rank_10_curr[1]
stan_input_lst$delta_1 <- rep(0.5,stan_input_lst$N_til)

fit_cohort_mmhp <- stan("../lib/model3_current.stan", 
                        ## this will need to be updated
                        data = stan_input_lst,
                        warmup = 10, iter = 200, chains = 4, thin=4,
                        control=list(adapt_delta=0.9,max_treedepth=15))
